---
title: "Week 11b Lecture"
author: "Mac"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Libraries

```{r}
library(tidyverse)
library(here)
library(gm)
```

# Load Data

```{r}
#tuesdata <- tidytuesdayR::tt_load(2021, week = 7)
#income_mean<-tuesdata$income_mean
income_mean <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-02-09/income_mean.csv')
```

# Data Analysis

Factor:

- a specialized version of a character
- how we truly store *categorical* data
- values of factors are called **levels**
- the default levels are always in alphabetical order
- make a factor by putting a vector into the function factor()

```{r}
fruits<-factor(c("Apple", "Grape", "Banana"))
fruits
```

If you have a typo in a column of what was supposed to be numbers, R will read everything in as characters. If the rows are characters and you try to convert them to numbers, rows with real characters will be coerced into NAs.

```{r}
test <- c("A", "1", "2")
as.numeric(test)
```

```{r}
test<-factor(test) # covert to factor
as.numeric(test)
```

forcats package:

- Family of functions for categorical data.
- All the main functions start with fct_

start with the starwars dataset to learn how to use factors

```{r}
glimpse(starwars)
```

# starwars

```{r}
starwars %>% 
  filter(!is.na(species)) %>% # remove the NAs
  count(species, sort = TRUE)
```

```{r}
star_counts<-starwars %>%
  filter(!is.na(species)) %>%
  mutate(species = fct_lump(species, n = 3)) %>%
  count(species)
star_counts
```

```{r}
star_counts %>%
  ggplot(aes(x = species, y = n)) +
  geom_col()
```

```{r}
star_counts %>%
  ggplot(aes(x = fct_reorder(species, n), y = n))+ # reorder the factor of species by n
  geom_col()
```

```{r}
star_counts %>%
  ggplot(aes(x = fct_reorder(species, n, .desc = TRUE), y = n)) + # reorder the factor of species by n
  geom_col() +
  labs(x = "Species")
```

```{r}
glimpse(income_mean)
```

```{r}
total_income<-income_mean %>%
  group_by(year, income_quintile) %>%
  summarise(income_dollars_sum = sum(income_dollars)) %>%
  mutate(income_quintile = factor(income_quintile)) # make it a factor
```

```{r}
total_income %>%
  ggplot(aes(x = year, y = income_dollars_sum, color = income_quintile)) +
  geom_line()
```

```{r}
total_income%>%
  ggplot(aes(x = year, y = income_dollars_sum, 
             color = fct_reorder2(income_quintile,year,income_dollars_sum)))+
  geom_line()+
  labs(color = "income quantile")
```

```{r}
x1 <- factor(c("Jan", "Mar", "Apr", "Dec"))
x1
```

```{r}
x1 <- factor(c("Jan", "Mar", "Apr", "Dec"), levels = c("Jan", "Mar", "Apr", "Dec"))
x1
```

```{r}
starwars_clean<-starwars %>% 
  filter(!is.na(species)) %>% # remove the NAs
  count(species, sort = TRUE) %>%
  mutate(species = factor(species)) %>% # make species a factor
  filter(n>3) # only keep species that have more than 3
starwars_clean
```

```{r}
levels(starwars_clean$species)
```

```{r}
starwars_clean<-starwars %>% 
  filter(!is.na(species)) %>% # remove the NAs
  count(species, sort = TRUE) %>%
  mutate(species = factor(species)) %>% # make species a factor 
  filter(n>3)  %>% # only keep species that have more than 3 
  droplevels() # drop extra levels
```

```{r}
levels(starwars_clean$species)
```

```{r}
starwars_clean<-starwars %>% 
  filter(!is.na(species)) %>% # remove the NAs
  count(species, sort = TRUE) %>%
  mutate(species = factor(species)) %>% # make species a factor 
  filter(n>3)  %>% # only keep species that have more than 3 
  droplevels() %>% # drop extra levels 
  mutate(species = fct_recode(species, "Humanoid" = "Human"))
starwars_clean
```

```{r}
# m <- Music() +  # initialize a Music object
#   Meter(4, 4) + # add a 4/4 time signature
#   Line(list("C5", "D5", "E5", "F5"), list(1, 1, 1, 1)) # add a musical line of four quarter notes
# show(m, to = c("score", "audio"))
```

