---
title: "Week 8b Lab"
author: "Mac"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Libraries

```{r}
library(tidyverse)
library(here)
library(maps)
library(mapdata)
library(mapproj)
library(ggmap)
library(ggsn)
library(patchwork)
library(ggrepel)
library(gganimate)
library(magick)
library(ggvis)
```

# Load Data

```{r}
ChemData <- read_csv(here("Week_09","Data","chemicaldata_maunalua.csv"))
ChemDataDictionary <- read_csv(here("Week_09","Data","chem_data_dictionary.csv"))
```

# Data Analysis

```{r}
View(ChemData)
View(ChemDataDictionary)
```

## mol_to_g: a function that converts mol, mmol, or umol to ug, mg, or g

silicate molar mass = 76.083 g/mol
phosphate molar mass = 94.9714 g/mol

v mol * (1 mol / 1 mol) = w mol, in_conv = 1
v mmol * (1 mol / 1000 mmol) = w mol, in_conv = 1/1000 = 0.001
v umol * (1 mol / 1000000 umol) = w mol, in_conv = 1/1000000 = 0.000001

w mol * x g/mol = y g

y g * (1 g / 1 g) = z g, out_conv = 1
y g * (1000 mg / 1 g) = z mg, out_conv = 1000
y g * (1000000 ug / 1 g) = z ug, out_conv = 1000000

```{r}
mol_to_g <- function(
    var_in, # variable to convert
    in_units, # convert from moles ("mol"), millimoles ("mmol"), or micromoles ("umol")
    mw, # molecular weight of substance
    out_units # convert to micrograms ("ug"), milligrams ("mg"), or grams ("g")
    ){
  if(in_units == "mol"){
    in_conv = 1
    }
  else if(in_units == "mmol"){
    in_conv = 0.001
    }
  else if(in_units == "umol"){
    in_conv = 0.000001
    }
  if(out_units == "g"){
    out_conv = 1
    }
  else if(out_units == "mg"){
    out_conv = 1000
    }
  else if(out_units == "ug"){
    out_conv = 1000000
    }
  var_out = var_in * in_conv * mw * out_conv
  return(var_out) # converted variable
  }
```

## Testing mol_to_g()

```{r}
mol_to_g(50, "mol", 100, "g")
mol_to_g(50, "mmol", 100, "g")
mol_to_g(50, "umol", 100, "g")
mol_to_g(50, "mol", 100, "mg")
mol_to_g(50, "mmol", 100, "mg")
mol_to_g(50, "umol", 100, "mg")
mol_to_g(50, "mol", 100, "ug")
mol_to_g(50, "mmol", 100, "ug")
mol_to_g(50, "umol", 100, "ug")
```

## map_point: a function that makes a ggmap of a chosen area, and then plots points over it based on a chosen dataset

```{r}
map_point <- function(
    lon, # longitude for base map
    lat, # latitude for base map
    data, # dataset to plot
    x, # column from dataset to plot on x axis 
    y, # column from dataset to plot on y axis 
    var, # column from dataset to represent at each point
    zoom, # zoom level of the map
    maptype = "satellite" # type for base map, satellite map by default
    ){
  # Make a data frame of lon and lat coordinates
  map_coor <- data.frame(lon = {{lon}}, lat = {{lat}})
  # Get base layer
  base_map <- get_map(map_coor, zoom = {{zoom}}, maptype = {{maptype}})
  # Plot it
  chem_map <- ggmap(base_map) +
    geom_point(data = {{data}}, aes(x = {{x}}, y = {{y}}, color = {{var}}), size = 4) +
    scale_color_viridis_c() +
    labs(x = "Longitude", y = "Latitude")
  return(chem_map)
  }
```

## Make converted columns for ChemData

```{r}
ChemData_converted <- ChemData %>%
  mutate(Phosphate_ug = mol_to_g(Phosphate, "umol", 94.9714, "ug")) %>%
  mutate(Phosphate_mg = mol_to_g(Phosphate, "umol", 94.9714, "mg")) %>%
  mutate(Phosphate_g = mol_to_g(Phosphate, "umol", 94.9714, "g")) %>%
  mutate(Silicate_ug = mol_to_g(Silicate, "umol", 76.083, "ug")) %>%
  mutate(Silicate_mg = mol_to_g(Silicate, "umol", 76.083, "mg")) %>%
  mutate(Silicate_g = mol_to_g(Silicate, "umol", 76.083, "g"))

View(ChemData_converted)
```

```{r}
phosphate_plot_umol <- map_point(lon = -157.7621, lat = 21.27427, data = ChemData_converted, x = Long, y = Lat, var = Phosphate, zoom = 17, maptype = "watercolor")

phosphate_plot_g <- map_point(lon = -157.7621, lat = 21.27427, data = ChemData_converted, x = Long, y = Lat, var = Phosphate_g, zoom = 17, maptype = "watercolor")

phosphate_plot_mg <- map_point(lon = -157.7621, lat = 21.27427, data = ChemData_converted, x = Long, y = Lat, var = Phosphate_mg, zoom = 17, maptype = "watercolor")

phosphate_plot_ug <- map_point(lon = -157.7621, lat = 21.27427, data = ChemData_converted, x = Long, y = Lat, var = Phosphate_ug, zoom = 17, maptype = "watercolor")

silicate_plot_umol <- map_point(lon = -157.7621, lat = 21.27427, data = ChemData_converted, x = Long, y = Lat, var = Silicate, zoom = 17, maptype = "watercolor")

silicate_plot_g <- map_point(lon = -157.7621, lat = 21.27427, data = ChemData_converted, x = Long, y = Lat, var = Silicate_g, zoom = 17, maptype = "watercolor")

silicate_plot_mg <- map_point(lon = -157.7621, lat = 21.27427, data = ChemData_converted, x = Long, y = Lat, var = Silicate_mg, zoom = 17, maptype = "watercolor")

silicate_plot_ug <- map_point(lon = -157.7621, lat = 21.27427, data = ChemData_converted, x = Long, y = Lat, var = Silicate_ug, zoom = 17, maptype = "watercolor")
```

```{r}
phosphate_plot_umol
```

```{r}
phosphate_plot_g 
```

```{r}
phosphate_plot_mg 
```

```{r}
phosphate_plot_ug
```

```{r}
silicate_plot_umol
```

```{r}
silicate_plot_g 
```

```{r}
silicate_plot_mg 
```

```{r}
silicate_plot_ug
```
