---
title: "Week 12a Lab"
author: "Mac"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

You have a set of 4 .csv files in data/homework. Each of these files is a timeseries of temperature and light data collected in tide pools in Oregon by Jenn Fields. Your goal is to bring in all 4 files and calculate the mean and standard deviation of both temperature (Temp.C) and light (Intensity.lux) for each tide pool. Use both a for loop and map() functions in your script. (Basically, do it twice). Due Tuesday at 1pm.

# Load Libraries

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(kableExtra)
```

### Data Dictionary

| Variable Name |	Description |
|:--------------|------------:|
| PoolID	      |ID of the pool|
| Foundation_spp |	Surfgrass or mussel dominated pool |
| Removal_Control	| Was it a removal or control treatment |
| Date.Time	| Date and time |
| Temp.C	| Temperature in degrees C |
| Intensity.lux	| Light level in lux |
| LoggerDepth	| Depth of the logger in meters |

# for loop

```{r}
TP1 <- read_csv(here("Week_12", "Data", "homework", "TP1.csv"))
TP2 <- read_csv(here("Week_12", "Data", "homework", "TP2.csv"))
TP3 <- read_csv(here("Week_12", "Data", "homework", "TP3.csv"))
TP4 <- read_csv(here("Week_12", "Data", "homework", "TP4.csv"))

View(TP1)
View(TP2)
View(TP3)
View(TP4)
```

```{r}
TidepoolPath <- here("Week_12", "Data", "homework") # location on the computer of the folder

# list all the files in that path with a specific pattern
# In this case we are looking for everything that has a .csv in the filename
# you can use regex to be more specific if you are looking for certain patterns in filenames

files <- dir(path = TidepoolPath, pattern = ".csv")

files
```

```{r}
# pre-allocate space

tidepool_data <- data.frame(matrix(nrow = length(files), ncol = 3)) # make an empty dataframe that has one row for each file and 3 columns

colnames(tidepool_data) <- c("filename", "mean_temp", "mean_light") # give the dataframe column names

kbl(tidepool_data) %>% kable_styling()
```

```{r}
for (i in 1:length(files)){ # loop over 1:3 the number of files 
raw_data <- read_csv(paste0(TidepoolPath, "/", files[i]))
tidepool_data$filename[i] <- files[i]
tidepool_data$mean_temp[i] <- mean(raw_data$Temp.C, na.rm = TRUE)
tidepool_data$mean_light[i] <- mean(raw_data$Intensity.lux, na.rm = TRUE)
tidepool_data$sd_temp[i] <- sd(raw_data$Temp.C, na.rm = TRUE)
tidepool_data$sd_light[i] <- sd(raw_data$Intensity.lux, na.rm = TRUE)
}

 kbl(tidepool_data) %>%
   kable_styling()
```

# map functions

```{r}
# point to the location on the computer of the folder

TidepoolPath <- here("Week_12", "Data", "homework")

files <- dir(path = TidepoolPath, pattern = ".csv")

files
```

```{r}
files <- dir(path = TidepoolPath, pattern = ".csv", full.names = TRUE) # save the entire path name

files
```

```{r}
tidepool_data_2 <- files %>%
  set_names() %>% # set's the id of each list to the file name
  map_df(read_csv, .id = "filename") %>% # map everything to a dataframe and put the id in a column called filename
  group_by(filename) %>%
  summarise(mean_temp = mean(Temp.C, na.rm = TRUE),
            mean_light = mean(Intensity.lux, na.rm = TRUE),
            sd_temp = sd(Temp.C, na.rm = TRUE),
            sd_light = sd(Intensity.lux, na.rm = TRUE))

kbl(tidepool_data_2) %>%
  kable_styling()
```

