---
title: "Week 8a Exercise"
author: "Mac"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Libraries

```{r}
library(tidyverse)
library(here)
library(patchwork)
library(ggrepel)
library(gganimate)
library(magick)
library(palmerpenguins)
```

# Data Analysis

## Patchwork

```{r}
# plot 1
p1<-penguins %>%
  ggplot(aes(x = body_mass_g, 
             y = bill_length_mm, 
             color = species))+
  geom_point()
p1

```

```{r}
# plot 2
p2<-penguins %>%
  ggplot(aes(x = sex, 
             y = body_mass_g, 
             color = species))+
  geom_jitter(width = 0.2)
p2
```

Adding two plots together

```{r}
p1+p2
```

Group the legends

```{r}
p1+p2 +
  plot_layout(guides = 'collect')
```

Add labels (A and B)

```{r}
p1+p2 +
  plot_layout(guides = 'collect')+
  plot_annotation(tag_levels = 'A')
```

put one plot on top of the other

```{r}
p1/p2 +
  plot_layout(guides = 'collect')+
  plot_annotation(tag_levels = 'A')
```

## ggrepel

```{r}
View(mtcars)
```

```{r}
ggplot(mtcars, aes(x = wt, 
                   y = mpg, 
                   label = rownames(mtcars))) +
  geom_text() + # creates a text label
  geom_point(color = 'red')
```

Repel the labels

```{r}
ggplot(mtcars, aes(x = wt, 
                   y = mpg, 
                   label = rownames(mtcars))) +
  geom_text_repel() + # repel them
  geom_point(color = 'red')
```

Use the label function

```{r}
ggplot(mtcars, aes(x = wt, 
                   y = mpg, 
                   label = rownames(mtcars))) +
  geom_label_repel() + # repel them
  geom_point(color = 'red')
```

## gganimate

```{r}
penguins %>%
ggplot(aes(x = body_mass_g, 
            y = bill_depth_mm, 
            color = species)) +
  geom_point()
```

Add a transition

```{r}
penguins %>%
ggplot(aes(x = body_mass_g, 
            y = bill_depth_mm, 
            color = species)) +
  geom_point() +
  transition_states(
     year, # what are we animating by
     transition_length = 2, #The relative length of the transition.
     state_length = 1 # The length of the pause between transitions
   )
```

Change the **ease** aesthetics

```{r}
penguins %>%
ggplot(aes(x = body_mass_g, 
            y = bill_depth_mm, 
            color = species)) +
  geom_point() +
  transition_states(
     year, # what are we animating by
     transition_length = 2, #The relative length of the transition.
     state_length = 1 # The length of the pause between transitions
   )+
  ease_aes("bounce-in-out")
```

Add a transition title

```{r}
penguins %>%
ggplot(aes(x = body_mass_g, 
            y = bill_depth_mm, 
            color = species)) +
  geom_point() +
  transition_states(
     year, # what are we animating by
     transition_length = 2, #The relative length of the transition.
     state_length = 1 # The length of the pause between transitions
   )+
  ease_aes("sine-in-out") +
  ggtitle('Year: {closest_state}')
```

Save it as a .gif

```{r}
penguins %>%
ggplot(aes(x = body_mass_g, 
            y = bill_depth_mm, 
            color = species)) +
  geom_point() +
  transition_states(
     year, # what are we animating by
     transition_length = 2, #The relative length of the transition.
     state_length = 1 # The length of the pause between transitions
   )+
  ease_aes("sine-in-out") +
  ggtitle('Year: {closest_state}') +
  anim_save(here("Week_08","Outputs","mypengiungif.gif"))
```

## magick

```{r}
penguin<-image_read("https://pngimg.com/uploads/penguin/pinguin_PNG9.png")
penguin
```

To put it on a plot you first need to save your plot as an image.

```{r}
penguins %>%
ggplot(aes(x = body_mass_g, 
            y = bill_depth_mm, 
            color = species)) +
  geom_point()
```

Read in the plot as a magick image and make a composite plot

```{r}
penplot<-image_read(here("Week_08","output","penguinplot.png"))
out <- image_composite(penplot, penguin, offset = "+70+30")
out
```

You can do this with gifs too.

```{r}
# Read in a penguin gif
pengif<-image_read("https://media3.giphy.com/media/H4uE6w9G1uK4M/giphy.gif")
outgif <- image_composite(penplot, pengif, gravity = "center")
animation <- image_animate(outgif, fps = 10, optimize = TRUE)
animation
```

Totally Awesome R Package

```{r}
library(sourrr)
build_recipe(final_weight = 900, hydration = 0.75)
```

